---
title: "Channel Conversion Flows Journey"
author: "Alan Millington"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Channel Conversion Flows

Adobe Analytics channel conversion flow data. Shows the different channels a user goes through before a conversion is made in each revenue funnel.

```{r Membership-Scatter-Plot, echo=FALSE, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
library(readr)
library(plotly)
library(RColorBrewer)
# Install adobeanayticsr from github
# devtools::install_github('benrwoodard/adobeanalyticsr', force = FALSE) 

library(adobeanalyticsr)
#Test Token has been refreshed and is upto date.
#aw_token()
rm(list = ls()) # Clear the environment before running the code
monitorStartTime_journey <- Sys.time()
#delete the aa.auth file in WD if issues

#Set Date range for Adobe Data pull below

#Last x days starting from yesterday
#date_range = c(Sys.Date() - 14, Sys.Date() - 1)

#Specific Start Date, End Date of yesterday.
date_range = c(as.Date("2021-06-17"), Sys.Date() - 1)

# Setup for Adobe Data
# aw_metrics <- aw_get_metrics()
# aw_dims <- aw_get_dimensions()
# aw_reportsuites <- aw_get_reportsuites()
# aw_calculatedmetrics <- aw_get_calculatedmetrics()
#  aw_segments <- aw_get_segments(
#   company_id = Sys.getenv("AW_COMPANY_ID"),
#   rsids = Sys.getenv("AW_REPORTSUITE_ID"),
#   segmentFilter = NA,
#   name = NA,
#   tagNames = NA,
#   filterByPublishedSegments = "all",
#   limit = 10000,
#   page = 0,
#   sortDirection = "DESC",
#   sortProperty = "modified_date",
#   expansion = NA,
#   includeType = "all",
#   debug = FALSE
# )
```

## Membership Scatter Plot

```{r membership-scatter-plot, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}

#Get the Adobe channel manager data using the 2.0 API from adobeanayticsr library
channel_stack_adobe <- aw_freeform_table(
  company_id = Sys.getenv("AW_COMPANY_ID"),
  rsid = Sys.getenv("AW_REPORTSUITE_ID"),
  date_range = date_range,
  dimensions = c("evar38"),
  metrics = c("event26","evar38instances"),
  top = c(50000),
  page = 0,
  filterType = "breakdown",
  segmentId = "s1957_6076f28b40d50e441ab3f0bd", # Segment Name: Membership Completion
  metricSort = "desc",
  include_unspecified = FALSE,
  search = NA,
  prettynames = FALSE,
  debug = FALSE
)

#load CSV
#channel_stacks <- read_csv("data/data-membership.csv", skip = 11)
channel_stacks <- channel_stack_adobe
colnames(channel_stacks) <- c("path", "conversion","path_count")

# Plot the scatter if needed (off for now)
p1 = plot_ly(
  channel_stacks,
  y=~conversion,
  x=~path_count,
  color=~conversion,
  size=~conversion,
  text=~path
) %>% layout(
  xaxis = list(type="log", title="Membership - Number of Paths"),
  yaxis = list(type="log", title="Membership - Number of Conversions")
) %>% colorbar(
  title = "Rate"
)
p1

```

## Membership Sankey Flow

```{r membership-sankey-flow, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}

channel_stacks$path_list = strsplit(x=channel_stacks$path,split=">")

#Set Depth Nodes - 4 or 5 seems optimum. no more than 6.
depth = 5

#Build the data into correct for mat for the Sankey
#Generate node labels and label length vectors
node_labels=rep(list(list()),depth)
label_length = list()
for(i in 1:depth){
  for(j in 1:length(channel_stacks$path)){
    if(!is.na(channel_stacks$path_list[j][[1]][i]))
      node_labels[[i]][j] = channel_stacks$path_list[j][[1]][i]
  }
  node_labels[[i]] = unique(unlist(node_labels[[i]]))
  node_labels[[i]] = node_labels[[i]][order(node_labels[[i]])]
  label_length[[i]] = length(node_labels[[i]])
}
node_labels = unlist(node_labels)
label_length = unlist(label_length)

#Build a data frame to fill out with each path view
combos = NULL
for(i in 1:(depth-1)){
  for(j in (1 + sum(label_length[1:i-1])):(label_length[i] + sum(label_length[1:i-1]))){
    for(k in (1 + label_length[i] + sum(label_length[1:i-1])):(label_length[i+1] + label_length[i] + sum(label_length[1:i-1]))){
      combos = rbind(combos, c(i,j,k,0))
    } 
  }
}
combos = as.data.frame(combos)
names(combos) = c("step","source","target","value")


#Populate the combo table
for(i in 1:(dim(combos)[1])){
  for(j in 1:(dim(channel_stacks)[1])){
    combos$value[i] = sum(combos$value[i], ifelse(
      (node_labels[combos$source[i]] == channel_stacks$path_list[j][[1]][combos$step[i]]) &
        (node_labels[combos$target[i]] == channel_stacks$path_list[j][[1]][combos$step[i]+1]),
      channel_stacks$path_count[j],0), na.rm = TRUE)
  }
}

#Add a node to populate with conversion values
uniques = unique(c(combos$source,combos$target))

converts = as.data.frame(list("step"=rep(0,length(uniques)), "source"=uniques, "target"=rep(max(uniques)+1,length(uniques)), 
                              "value"=rep(0,length(uniques))))
combos = rbind(combos,converts)
for(i in 1:(dim(channel_stacks)[1])){
  stack_depth = min(depth,length(channel_stacks$path_list[i][[1]]))
  index_val = which(combos$step==0 & combos$source==(which(node_labels == channel_stacks$path_list[i][[1]][stack_depth]) + 
                                                       ifelse(stack_depth>1, sum(label_length[1:(stack_depth-1)]),0)))
  combos$value[index_val] = combos$value[index_val] + channel_stacks$conversion[i]
}
#Populate the conversion node values
display_node_labels = node_labels
for(i in 1:length(label_length)){
  for(j in 1:label_length[i]){
    display_node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))] = paste0(i,":",node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))])
  }
}
display_node_labels = c(display_node_labels, "Conversion")
#Prep the Sankey Title based on Date and Channel
sankey_title <- paste("Channel Conversion Flow - Membership Sales ", date_range[1], "-", date_range[2])

#Generate Sankey diagram
p2 <- plot_ly(
  type = "sankey",
  orientation = "h",
  node = list(
    label = display_node_labels,
    #color = node_colors,
    pad = 10,
    alpha = 0.9,
    thickness = 20,
    line = list(
      color = "black",
      width = 0.1
    )
  ),
  
  link = list(
    source = combos$source-1, # convert to zero index
    target = combos$target-1, # convert to zero index
    value = combos$value, #size of connection
    color = 'rgba(0,0,0,0.1)'
    #color = combos$color #add colors for each link if desired
  )
) %>% 
  layout(
    title = sankey_title,
    font = list(
      size = 10
    )
  )
p2
```

## Membership Renewals Scatter Plot

```{r membership-renewals-scatter-plot, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}

#Get the Adobe channel manager data using the 2.0 API from adobeanayticsr library
channel_stack_adobe <- aw_freeform_table(
  company_id = Sys.getenv("AW_COMPANY_ID"),
  rsid = Sys.getenv("AW_REPORTSUITE_ID"),
  date_range = date_range,
  dimensions = c("evar38"),
  metrics = c("event73","evar38instances"),
  top = c(50000),
  page = 0,
  filterType = "breakdown",
  segmentId = "s1957_6076f79f1786ec6aa730cdbc", # Segment Name: Membership Renewal Completion
  metricSort = "desc",
  include_unspecified = FALSE,
  search = NA,
  prettynames = FALSE,
  debug = FALSE
)

#load CSV
#channel_stacks <- read_csv("data/data-membership.csv", skip = 11)
channel_stacks <- channel_stack_adobe
colnames(channel_stacks) <- c("path", "conversion","path_count")

# Plot the scatter if needed (off for now)
p1 = plot_ly(
  channel_stacks,
  y=~conversion,
  x=~path_count,
  color=~conversion,
  size=~conversion,
  text=~path
) %>% layout(
  xaxis = list(type="log", title="Membership Renewals - Number of Paths"),
  yaxis = list(type="log", title="Membership Renewals - Number of Conversions")
) %>% colorbar(
  title = "Rate"
)
p1

```

## Membership Renewals Sankey Flow

```{r membership-renewals-sankey-plot, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
channel_stacks$path_list = strsplit(x=channel_stacks$path,split=">")

#Set Depth Nodes - 4 or 5 seems optimum. no more than 6.
depth = 5

#Build the data into correct for mat for the Sankey
#Generate node labels and label length vectors
node_labels=rep(list(list()),depth)
label_length = list()
for(i in 1:depth){
  for(j in 1:length(channel_stacks$path)){
    if(!is.na(channel_stacks$path_list[j][[1]][i]))
      node_labels[[i]][j] = channel_stacks$path_list[j][[1]][i]
  }
  node_labels[[i]] = unique(unlist(node_labels[[i]]))
  node_labels[[i]] = node_labels[[i]][order(node_labels[[i]])]
  label_length[[i]] = length(node_labels[[i]])
}
node_labels = unlist(node_labels)
label_length = unlist(label_length)

#Build a data frame to fill out with each path view
combos = NULL
for(i in 1:(depth-1)){
  for(j in (1 + sum(label_length[1:i-1])):(label_length[i] + sum(label_length[1:i-1]))){
    for(k in (1 + label_length[i] + sum(label_length[1:i-1])):(label_length[i+1] + label_length[i] + sum(label_length[1:i-1]))){
      combos = rbind(combos, c(i,j,k,0))
    } 
  }
}
combos = as.data.frame(combos)
names(combos) = c("step","source","target","value")


#Populate the combo table
for(i in 1:(dim(combos)[1])){
  for(j in 1:(dim(channel_stacks)[1])){
    combos$value[i] = sum(combos$value[i], ifelse(
      (node_labels[combos$source[i]] == channel_stacks$path_list[j][[1]][combos$step[i]]) &
        (node_labels[combos$target[i]] == channel_stacks$path_list[j][[1]][combos$step[i]+1]),
      channel_stacks$path_count[j],0), na.rm = TRUE)
  }
}

#Add a node to populate with conversion values
uniques = unique(c(combos$source,combos$target))

converts = as.data.frame(list("step"=rep(0,length(uniques)), "source"=uniques, "target"=rep(max(uniques)+1,length(uniques)), 
                              "value"=rep(0,length(uniques))))
combos = rbind(combos,converts)
for(i in 1:(dim(channel_stacks)[1])){
  stack_depth = min(depth,length(channel_stacks$path_list[i][[1]]))
  index_val = which(combos$step==0 & combos$source==(which(node_labels == channel_stacks$path_list[i][[1]][stack_depth]) + 
                                                       ifelse(stack_depth>1, sum(label_length[1:(stack_depth-1)]),0)))
  combos$value[index_val] = combos$value[index_val] + channel_stacks$conversion[i]
}
#Populate the conversion node values
display_node_labels = node_labels
for(i in 1:length(label_length)){
  for(j in 1:label_length[i]){
    display_node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))] = paste0(i,":",node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))])
  }
}
display_node_labels = c(display_node_labels, "Conversion")
#Prep the Sankey Title based on Date and Channel
sankey_title <- paste("Channel Conversion Flow - Membership Renewals ", date_range[1], "-", date_range[2])

#Generate Sankey diagram
p2 <- plot_ly(
  type = "sankey",
  orientation = "h",
  node = list(
    label = display_node_labels,
    #color = node_colors,
    pad = 10,
    alpha = 0.9,
    thickness = 20,
    line = list(
      color = "black",
      width = 0.1
    )
  ),
  
  link = list(
    source = combos$source-1, # convert to zero index
    target = combos$target-1, # convert to zero index
    value = combos$value, #size of connection
    color = 'rgba(0,0,0,0.1)'
    #color = combos$color #add colors for each link if desired
  )
) %>% 
  layout(
    title = sankey_title,
    font = list(
      size = 10
    )
  )
p2
```

## Holidays Scatter Plot

```{r holidays-scatter-plot, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
#Get the Adobe channel manager data using the 2.0 API from adobeanayticsr library
channel_stack_adobe <- aw_freeform_table(
  company_id = Sys.getenv("AW_COMPANY_ID"),
  rsid = Sys.getenv("AW_REPORTSUITE_ID"),
  date_range = date_range,
  dimensions = c("evar38"),
  metrics = c("event134","evar38instances"),
  top = c(50000),
  page = 0,
  filterType = "breakdown",
  segmentId = "s1957_6076f8100e41ff781cd16ed3", # Segment Name: Holiday Booking Completion
  metricSort = "desc",
  include_unspecified = FALSE,
  search = NA,
  prettynames = FALSE,
  debug = FALSE
)

#load CSV
#channel_stacks <- read_csv("data/data-membership.csv", skip = 11)
channel_stacks <- channel_stack_adobe
colnames(channel_stacks) <- c("path", "conversion","path_count")

# Plot the scatter if needed (off for now)
p1 = plot_ly(
  channel_stacks,
  y=~conversion,
  x=~path_count,
  color=~conversion,
  size=~conversion,
  text=~path
) %>% layout(
  xaxis = list(type="log", title="Holidays - Number of Paths"),
  yaxis = list(type="log", title="Holidays - Number of Conversions")
) %>% colorbar(
  title = "Rate"
)
p1
```

## Holidays Sankey Flow

```{r holidays-sankey-flow, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
channel_stacks$path_list = strsplit(x=channel_stacks$path,split=">")

#Set Depth Nodes - 4 or 5 seems optimum. no more than 6.
depth = 5

#Build the data into correct for mat for the Sankey
#Generate node labels and label length vectors
node_labels=rep(list(list()),depth)
label_length = list()
for(i in 1:depth){
  for(j in 1:length(channel_stacks$path)){
    if(!is.na(channel_stacks$path_list[j][[1]][i]))
      node_labels[[i]][j] = channel_stacks$path_list[j][[1]][i]
  }
  node_labels[[i]] = unique(unlist(node_labels[[i]]))
  node_labels[[i]] = node_labels[[i]][order(node_labels[[i]])]
  label_length[[i]] = length(node_labels[[i]])
}
node_labels = unlist(node_labels)
label_length = unlist(label_length)

#Build a data frame to fill out with each path view
combos = NULL
for(i in 1:(depth-1)){
  for(j in (1 + sum(label_length[1:i-1])):(label_length[i] + sum(label_length[1:i-1]))){
    for(k in (1 + label_length[i] + sum(label_length[1:i-1])):(label_length[i+1] + label_length[i] + sum(label_length[1:i-1]))){
      combos = rbind(combos, c(i,j,k,0))
    } 
  }
}
combos = as.data.frame(combos)
names(combos) = c("step","source","target","value")


#Populate the combo table
for(i in 1:(dim(combos)[1])){
  for(j in 1:(dim(channel_stacks)[1])){
    combos$value[i] = sum(combos$value[i], ifelse(
      (node_labels[combos$source[i]] == channel_stacks$path_list[j][[1]][combos$step[i]]) &
        (node_labels[combos$target[i]] == channel_stacks$path_list[j][[1]][combos$step[i]+1]),
      channel_stacks$path_count[j],0), na.rm = TRUE)
  }
}

#Add a node to populate with conversion values
uniques = unique(c(combos$source,combos$target))

converts = as.data.frame(list("step"=rep(0,length(uniques)), "source"=uniques, "target"=rep(max(uniques)+1,length(uniques)), 
                              "value"=rep(0,length(uniques))))
combos = rbind(combos,converts)
for(i in 1:(dim(channel_stacks)[1])){
  stack_depth = min(depth,length(channel_stacks$path_list[i][[1]]))
  index_val = which(combos$step==0 & combos$source==(which(node_labels == channel_stacks$path_list[i][[1]][stack_depth]) + 
                                                       ifelse(stack_depth>1, sum(label_length[1:(stack_depth-1)]),0)))
  combos$value[index_val] = combos$value[index_val] + channel_stacks$conversion[i]
}
#Populate the conversion node values
display_node_labels = node_labels
for(i in 1:length(label_length)){
  for(j in 1:label_length[i]){
    display_node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))] = paste0(i,":",node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))])
  }
}
display_node_labels = c(display_node_labels, "Conversion")
#Prep the Sankey Title based on Date and Channel
sankey_title <- paste("Channel Conversion Flow - Holiday Sales ", date_range[1], "-", date_range[2])

#Generate Sankey diagram
p2 <- plot_ly(
  type = "sankey",
  orientation = "h",
  node = list(
    label = display_node_labels,
    #color = node_colors,
    pad = 10,
    alpha = 0.9,
    thickness = 20,
    line = list(
      color = "black",
      width = 0.1
    )
  ),
  
  link = list(
    source = combos$source-1, # convert to zero index
    target = combos$target-1, # convert to zero index
    value = combos$value, #size of connection
    color = 'rgba(0,0,0,0.1)'
    #color = combos$color #add colors for each link if desired
  )
) %>% 
  layout(
    title = sankey_title,
    font = list(
      size = 10
    )
  )
p2
```

## Shop Scatter Plot

```{r shop-scatter-plot, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
#Get the Adobe channel manager data using the 2.0 API from adobeanayticsr library
channel_stack_adobe <- aw_freeform_table(
  company_id = Sys.getenv("AW_COMPANY_ID"),
  rsid = Sys.getenv("AW_REPORTSUITE_ID"),
  date_range = date_range,
  dimensions = c("evar38"),
  metrics = c("event182","evar38instances"),
  top = c(50000),
  page = 0,
  filterType = "breakdown",
  segmentId = "s1957_6076f7deb2029b591cf20e4a", # Segment Name: Shop Order Completion
  metricSort = "desc",
  include_unspecified = FALSE,
  search = NA,
  prettynames = FALSE,
  debug = FALSE
)

#load CSV
#channel_stacks <- read_csv("data/data-membership.csv", skip = 11)
channel_stacks <- channel_stack_adobe
colnames(channel_stacks) <- c("path", "conversion","path_count")

# Plot the scatter if needed (off for now)
p1 = plot_ly(
  channel_stacks,
  y=~conversion,
  x=~path_count,
  color=~conversion,
  size=~conversion,
  text=~path
) %>% layout(
  xaxis = list(type="log", title="Shop - Number of Paths"),
  yaxis = list(type="log", title="Shop - Number of Conversions")
) %>% colorbar(
  title = "Rate"
)
p1
```

## Shop Sankey Flow

```{r shop-sankey-flow, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
channel_stacks$path_list = strsplit(x=channel_stacks$path,split=">")
depth = 5

#Generate node labels and label length vectors
node_labels=rep(list(list()),depth)
label_length = list()
for(i in 1:depth){
  for(j in 1:length(channel_stacks$path)){
    if(!is.na(channel_stacks$path_list[j][[1]][i]))
      node_labels[[i]][j] = channel_stacks$path_list[j][[1]][i]
  }
  node_labels[[i]] = unique(unlist(node_labels[[i]]))
  node_labels[[i]] = node_labels[[i]][order(node_labels[[i]])]
  label_length[[i]] = length(node_labels[[i]])
}
node_labels = unlist(node_labels)
label_length = unlist(label_length)

#Build a data frame to fill out with each path view
combos = NULL
for(i in 1:(depth-1)){
  for(j in (1 + sum(label_length[1:i-1])):(label_length[i] + sum(label_length[1:i-1]))){
    for(k in (1 + label_length[i] + sum(label_length[1:i-1])):(label_length[i+1] + label_length[i] + sum(label_length[1:i-1]))){
      combos = rbind(combos, c(i,j,k,0))
    } 
  }
}
combos = as.data.frame(combos)
names(combos) = c("step","source","target","value")


#Populate the combo table
for(i in 1:(dim(combos)[1])){
  for(j in 1:(dim(channel_stacks)[1])){
    combos$value[i] = sum(combos$value[i], ifelse(
      (node_labels[combos$source[i]] == channel_stacks$path_list[j][[1]][combos$step[i]]) &
        (node_labels[combos$target[i]] == channel_stacks$path_list[j][[1]][combos$step[i]+1]),
      channel_stacks$path_count[j],0), na.rm = TRUE)
  }
}
#OK to here
#Add a node to populate with conversion values
uniques = unique(c(combos$source,combos$target))

converts = as.data.frame(list("step"=rep(0,length(uniques)), "source"=uniques, "target"=rep(max(uniques)+1,length(uniques)), 
                              "value"=rep(0,length(uniques))))
combos = rbind(combos,converts)
for(i in 1:(dim(channel_stacks)[1])){
  stack_depth = min(depth,length(channel_stacks$path_list[i][[1]]))
  index_val = which(combos$step==0 & combos$source==(which(node_labels == channel_stacks$path_list[i][[1]][stack_depth]) + 
                                                       ifelse(stack_depth>1, sum(label_length[1:(stack_depth-1)]),0)))
  combos$value[index_val] = combos$value[index_val] + channel_stacks$conversion[i]
}
#Populate the conversion node values
display_node_labels = node_labels
for(i in 1:length(label_length)){
  for(j in 1:label_length[i]){
    display_node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))] = paste0(i,":",node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))])
  }
}
display_node_labels = c(display_node_labels, "Conversion")
#Prep the Sankey Title based on Date and Channel
sankey_title <- paste("Channel Conversion Flow - Shop Sales ", date_range[1], "-", date_range[2])

#Generate Sankey diagram
s2 <- plot_ly(
  type = "sankey",
  orientation = "h",
  
  node = list(
    label = display_node_labels,
   #color = node_colors,
    pad = 10,
   alpha = 0.9,
    thickness = 20,
    line = list(
      color = "black",
      width = 0.1
    )
  ),
  
  link = list(
    source = combos$source-1, # convert to zero index
    target = combos$target-1, # convert to zero index
    value = combos$value, #size of connection
    color = 'rgba(0,0,0,0.1)'
    #color = combos$color #add colors for each link if desired
  )
) %>% 
  layout(
    title = sankey_title,
    font = list(
      size = 10
    )
  )
s2
```


## Donations Scatter Plot

```{r donations-scatter-plot, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
#Get the Adobe channel manager data using the 2.0 API from adobeanayticsr library
channel_stack_adobe <- aw_freeform_table(
  company_id = Sys.getenv("AW_COMPANY_ID"),
  rsid = Sys.getenv("AW_REPORTSUITE_ID"),
  date_range = date_range,
  dimensions = c("evar38"),
  metrics = c("event116","evar38instances"),
  top = c(50000),
  page = 0,
  filterType = "breakdown",
  segmentId = "s1957_6076f83b0e41ff781cd16ed5", # Segment Name: Donation Completion
  metricSort = "desc",
  include_unspecified = FALSE,
  search = NA,
  prettynames = FALSE,
  debug = FALSE
)

#load CSV
#channel_stacks <- read_csv("data/data-membership.csv", skip = 11)
channel_stacks <- channel_stack_adobe
colnames(channel_stacks) <- c("path", "conversion","path_count")

# Plot the scatter if needed (off for now)
p1 = plot_ly(
  channel_stacks,
  y=~conversion,
  x=~path_count,
  color=~conversion,
  size=~conversion,
  text=~path
) %>% layout(
  xaxis = list(type="log", title="Donations - Number of Paths"),
  yaxis = list(type="log", title="Donations - Number of Conversions")
) %>% colorbar(
  title = "Rate"
)
p1
```

## Donations Sankey Flow

```{r donations-sankey-flow, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}

channel_stacks$path_list = strsplit(x=channel_stacks$path,split=">")

#Set Depth Nodes - 4 or 5 seems optimum. no more than 6.
depth = 5

#Build the data into correct for mat for the Sankey
#Generate node labels and label length vectors
node_labels=rep(list(list()),depth)
label_length = list()
for(i in 1:depth){
  for(j in 1:length(channel_stacks$path)){
    if(!is.na(channel_stacks$path_list[j][[1]][i]))
      node_labels[[i]][j] = channel_stacks$path_list[j][[1]][i]
  }
  node_labels[[i]] = unique(unlist(node_labels[[i]]))
  node_labels[[i]] = node_labels[[i]][order(node_labels[[i]])]
  label_length[[i]] = length(node_labels[[i]])
}
node_labels = unlist(node_labels)
label_length = unlist(label_length)

#Build a data frame to fill out with each path view
combos = NULL
for(i in 1:(depth-1)){
  for(j in (1 + sum(label_length[1:i-1])):(label_length[i] + sum(label_length[1:i-1]))){
    for(k in (1 + label_length[i] + sum(label_length[1:i-1])):(label_length[i+1] + label_length[i] + sum(label_length[1:i-1]))){
      combos = rbind(combos, c(i,j,k,0))
    } 
  }
}
combos = as.data.frame(combos)
names(combos) = c("step","source","target","value")


#Populate the combo table
for(i in 1:(dim(combos)[1])){
  for(j in 1:(dim(channel_stacks)[1])){
    combos$value[i] = sum(combos$value[i], ifelse(
      (node_labels[combos$source[i]] == channel_stacks$path_list[j][[1]][combos$step[i]]) &
        (node_labels[combos$target[i]] == channel_stacks$path_list[j][[1]][combos$step[i]+1]),
      channel_stacks$path_count[j],0), na.rm = TRUE)
  }
}

#Add a node to populate with conversion values
uniques = unique(c(combos$source,combos$target))

converts = as.data.frame(list("step"=rep(0,length(uniques)), "source"=uniques, "target"=rep(max(uniques)+1,length(uniques)), 
                              "value"=rep(0,length(uniques))))
combos = rbind(combos,converts)
for(i in 1:(dim(channel_stacks)[1])){
  stack_depth = min(depth,length(channel_stacks$path_list[i][[1]]))
  index_val = which(combos$step==0 & combos$source==(which(node_labels == channel_stacks$path_list[i][[1]][stack_depth]) + 
                                                       ifelse(stack_depth>1, sum(label_length[1:(stack_depth-1)]),0)))
  combos$value[index_val] = combos$value[index_val] + channel_stacks$conversion[i]
}
#Populate the conversion node values
display_node_labels = node_labels
for(i in 1:length(label_length)){
  for(j in 1:label_length[i]){
    display_node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))] = paste0(i,":",node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))])
  }
}
display_node_labels = c(display_node_labels, "Conversion")
#Prep the Sankey Title based on Date and Channel
sankey_title <- paste("Channel Conversion Flow - Donations ", date_range[1], "-", date_range[2])

#Generate Sankey diagram
p2 <- plot_ly(
  type = "sankey",
  orientation = "h",
  node = list(
    label = display_node_labels,
    #color = node_colors,
    pad = 10,
    alpha = 0.9,
    thickness = 20,
    line = list(
      color = "black",
      width = 0.1
    )
  ),
  
  link = list(
    source = combos$source-1, # convert to zero index
    target = combos$target-1, # convert to zero index
    value = combos$value, #size of connection
    color = 'rgba(0,0,0,0.1)'
    #color = combos$color #add colors for each link if desired
  )
) %>% 
  layout(
    title = sankey_title,
    font = list(
      size = 10
    )
  )
p2
```

## Event Booking Clicks to Eventbrite/DigiTickets  Scatter Plot

```{r event-booking-scatter-plot, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}
#Get the Adobe channel manager data using the 2.0 API from adobeanayticsr library
channel_stack_adobe <- aw_freeform_table(
  company_id = Sys.getenv("AW_COMPANY_ID"),
  rsid = Sys.getenv("AW_REPORTSUITE_ID"),
  date_range = date_range,
  dimensions = c("evar38"),
  metrics = c("event57","evar38instances"),
  top = c(50000),
  page = 0,
  filterType = "breakdown",
  segmentId = "s1957_60dc585bb5632031603f2318", # Segment Name: Event Booking Click Completion
  metricSort = "desc",
  include_unspecified = FALSE,
  search = NA,
  prettynames = FALSE,
  debug = FALSE
)

#load CSV
#channel_stacks <- read_csv("data/data-membership.csv", skip = 11)
channel_stacks <- channel_stack_adobe
colnames(channel_stacks) <- c("path", "conversion","path_count")

# Plot the scatter if needed (off for now)
p1 = plot_ly(
  channel_stacks,
  y=~conversion,
  x=~path_count,
  color=~conversion,
  size=~conversion,
  text=~path
) %>% layout(
  xaxis = list(type="log", title="Event Booking - Number of Paths"),
  yaxis = list(type="log", title="Event Booking - Number of Conversions")
) %>% colorbar(
  title = "Rate"
)
p1
```

## Event Booking Sankey Flow

```{r event-booking-sankey-flow, fig.height=9, fig.width=11, message=FALSE, warning=FALSE}

channel_stacks$path_list = strsplit(x=channel_stacks$path,split=">")

#Set Depth Nodes - 4 or 5 seems optimum. no more than 6.
depth = 5

#Build the data into correct for mat for the Sankey
#Generate node labels and label length vectors
node_labels=rep(list(list()),depth)
label_length = list()
for(i in 1:depth){
  for(j in 1:length(channel_stacks$path)){
    if(!is.na(channel_stacks$path_list[j][[1]][i]))
      node_labels[[i]][j] = channel_stacks$path_list[j][[1]][i]
  }
  node_labels[[i]] = unique(unlist(node_labels[[i]]))
  node_labels[[i]] = node_labels[[i]][order(node_labels[[i]])]
  label_length[[i]] = length(node_labels[[i]])
}
node_labels = unlist(node_labels)
label_length = unlist(label_length)

#Build a data frame to fill out with each path view
combos = NULL
for(i in 1:(depth-1)){
  for(j in (1 + sum(label_length[1:i-1])):(label_length[i] + sum(label_length[1:i-1]))){
    for(k in (1 + label_length[i] + sum(label_length[1:i-1])):(label_length[i+1] + label_length[i] + sum(label_length[1:i-1]))){
      combos = rbind(combos, c(i,j,k,0))
    } 
  }
}
combos = as.data.frame(combos)
names(combos) = c("step","source","target","value")


#Populate the combo table
for(i in 1:(dim(combos)[1])){
  for(j in 1:(dim(channel_stacks)[1])){
    combos$value[i] = sum(combos$value[i], ifelse(
      (node_labels[combos$source[i]] == channel_stacks$path_list[j][[1]][combos$step[i]]) &
        (node_labels[combos$target[i]] == channel_stacks$path_list[j][[1]][combos$step[i]+1]),
      channel_stacks$path_count[j],0), na.rm = TRUE)
  }
}

#Add a node to populate with conversion values
uniques = unique(c(combos$source,combos$target))

converts = as.data.frame(list("step"=rep(0,length(uniques)), "source"=uniques, "target"=rep(max(uniques)+1,length(uniques)), 
                              "value"=rep(0,length(uniques))))
combos = rbind(combos,converts)
for(i in 1:(dim(channel_stacks)[1])){
  stack_depth = min(depth,length(channel_stacks$path_list[i][[1]]))
  index_val = which(combos$step==0 & combos$source==(which(node_labels == channel_stacks$path_list[i][[1]][stack_depth]) + 
                                                       ifelse(stack_depth>1, sum(label_length[1:(stack_depth-1)]),0)))
  combos$value[index_val] = combos$value[index_val] + channel_stacks$conversion[i]
}
#Populate the conversion node values
display_node_labels = node_labels
for(i in 1:length(label_length)){
  for(j in 1:label_length[i]){
    display_node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))] = paste0(i,":",node_labels[j+ifelse(i==1,0,sum(label_length[1:(i-1)]))])
  }
}
display_node_labels = c(display_node_labels, "Conversion")
#Prep the Sankey Title based on Date and Channel
sankey_title <- paste("Channel Conversion Flow - Event Booking ", date_range[1], "-", date_range[2])

#Generate Sankey diagram
p2 <- plot_ly(
  type = "sankey",
  orientation = "h",
  node = list(
    label = display_node_labels,
    #color = node_colors,
    pad = 10,
    alpha = 0.9,
    thickness = 20,
    line = list(
      color = "black",
      width = 0.1
    )
  ),
  
  link = list(
    source = combos$source-1, # convert to zero index
    target = combos$target-1, # convert to zero index
    value = combos$value, #size of connection
    color = 'rgba(0,0,0,0.1)'
    #color = combos$color #add colors for each link if desired
  )
) %>% 
  layout(
    title = sankey_title,
    font = list(
      size = 10
    )
  )
p2
```



```{r run-time, include=FALSE}
monitorEndTime_journey <- Sys.time()
# Write out to the console how long it took for the entire process to run.
lastrunTime_journey <- paste0("This process took ",monitorEndTime_journey - monitorStartTime_journey," minutes to run.",sep=" ")
lastrunTime_journey
```